Import libraries
```{r}
library(tidyverse)
library(ggplot2)
library(arules)
library(arulesViz)
library(kernlab)
library(caret)
```

Import Dataset
```{r}
db <- read_csv('https://intro-datascience.s3.us-east-2.amazonaws.com/Resort01.csv')
```

Statistically examine data using summary
```{r}
summary(db)
```

str()/glimpse() to check for data redundancies
```{r}
glimpse(db)
```
Convert non-numeric to factor in the copy of the db
```{r}
db_c <- db
db_c$IsCanceled <- as.factor(db_c$IsCanceled)
db_c$Meal <- as.factor(db_c$Meal)
db_c$Country <- as.factor(db_c$Country)
db_c$MarketSegment <- as.factor(db_c$MarketSegment)
db_c$IsRepeatedGuest <- as.factor(db_c$IsRepeatedGuest)
db_c$ReservedRoomType <- as.factor(db_c$ReservedRoomType)
db_c$AssignedRoomType <- as.factor(db_c$AssignedRoomType)
db_c$DepositType <- as.factor(db_c$DepositType)
db_c$CustomerType <- as.factor(db_c$CustomerType)
str(db_c)
```
Check for outliers in data
```{r}
bplt <- ggplot(db)+ aes(x=IsCanceled)
bplt1 <- bplt+aes(y = LeadTime, group = IsCanceled) + geom_boxplot()
bplt1
bplt2 <- bplt + aes(y = PreviousCancellations, group = IsCanceled) + geom_boxplot()
bplt2
bplt3 <- bplt + aes(y = PreviousBookingsNotCanceled, group = IsCanceled) + geom_boxplot()
bplt3
bplt4 <- bplt + aes(y = BookingChanges, group = IsCanceled) + geom_boxplot()
bplt4
bplt5 <- bplt + aes(y = TotalOfSpecialRequests, group = IsCanceled) + geom_boxplot()
bplt5
bplt6 <- bplt + aes(y = StaysInWeekendNights, group = IsCanceled) + geom_boxplot()
bplt6
bplt7 <- bplt + aes(y = StaysInWeekNights, group = IsCanceled) + geom_boxplot()
bplt7
bplt8 <- bplt + aes(y = RequiredCarParkingSpaces, group = IsCanceled) + geom_boxplot()
bplt8
bplt9 <- bplt + aes(y = Adults, group = IsCanceled) + geom_boxplot()
bplt9
```

Scatter plots to see linear relations or others
```{r}
cplt <- ggplot(db) + aes(x = IsCanceled)
cplt1 <- cplt + aes(y = IsRepeatedGuest) + geom_count()
cplt1
cplt2 <- cplt + aes(y = Meal) + geom_count()
cplt2
cplt3 <- cplt + aes(y = MarketSegment) + geom_count()
cplt3
cplt4 <- cplt + aes(y = CustomerType) + geom_count()
cplt4

catDB <- as(db_c[,c("IsCanceled", "Meal", "MarketSegment", "IsRepeatedGuest", "DepositType", "CustomerType")], "transactions")
ctab <- crossTable(catDB, sort = TRUE)
ctCan <- ctab[,c("IsCanceled=0", "IsCanceled=1")]
ctCan
```
Using crosstab data
```{r}
ctCanDF <- data.frame(ctCan)
ctCanDF$total <- ctCanDF$IsCanceled.0 + ctCanDF$IsCanceled.1
ctCanDF$IsCanceled.0 <- ctCanDF$IsCanceled.0*100/ctCanDF$total
ctCanDF$IsCanceled.1 <- ctCanDF$IsCanceled.1*100/ctCanDF$total
ctCanDF$total <- ctCanDF$total*100/40060
```
Tidying crosstable data
```{r}
ctDF <- t(ctCanDF[,c("IsCanceled.1", "IsCanceled.0")])
row.names(ctDF)[row.names(ctDF) == "IsCanceled.1"] <- "IsCanceled"
row.names(ctDF)[row.names(ctDF) == "IsCanceled.0"] <- "IsNotCanceled"
n <- c("NotARepeatGuest", "NoDeposit", "TransientCustomer", "Bed&Breakfast", "NotCanceled", "OnlineTA", "Canceled", "Halfboard", "TransientParty", "OfflineTATO", "DirectMarketSeg", "GroupMarketSeg", "CorporateMarketSeg", "RepeatGuest", "ContractCustomer", "NoRefundDeposit", "UnknownMeal", "Fullboard", "GroupCustomer", "ComplementaryMarketSeg", "RefundableDeposit", "NoMeal")
colnames(ctDF) <- n
ctDF <- round(subset(ctDF, select=-c(Canceled, NotCanceled)), digits=2)
```

Subsetting and barplots
```{r}
brplt1 <- barplot(ctDF[,c("NotARepeatGuest", "RepeatGuest")],beside =TRUE, ylab = "% of total people", ylim = c(0,110.00))
text(brplt1, y = ctDF[,c("NotARepeatGuest", "RepeatGuest")],
     label = array(ctDF[,c("NotARepeatGuest", "RepeatGuest")]),pos = 3,cex = 0.8)

brplt2 <- barplot(ctDF[,c("NoDeposit", "NoRefundDeposit", "RefundableDeposit")],beside =TRUE, ylab = "% of total people", ylim = c(0,110.00))
text(brplt2, y = ctDF[,c("NoDeposit", "NoRefundDeposit", "RefundableDeposit")],
     label = array(ctDF[,c("NoDeposit", "NoRefundDeposit", "RefundableDeposit")]),pos = 3,cex = 0.8)

brplt3 <- barplot(ctDF[,c("TransientCustomer", "TransientParty", "ContractCustomer", "GroupCustomer")]
                  ,beside =TRUE, ylab = "% of total people", ylim = c(0,110.00))
text(brplt3, y = ctDF[,c("TransientCustomer", "TransientParty", "ContractCustomer", "GroupCustomer")],
     label = array(ctDF[,c("TransientCustomer", "TransientParty", "ContractCustomer", "GroupCustomer")]),pos = 3,cex = 0.8)

brplt4 <- barplot(ctDF[,c("OnlineTA", "OfflineTATO", "DirectMarketSeg", "GroupMarketSeg", "CorporateMarketSeg", "ComplementaryMarketSeg")], names.arg=c("Online TA", "Offline", "Direct", "Group", "Corporate", "Compl"), beside =TRUE, ylab = "% of total people", ylim = c(0,110.00))
text(brplt4, y = ctDF[,c("OnlineTA", "OfflineTATO", "DirectMarketSeg", "GroupMarketSeg", "CorporateMarketSeg", "ComplementaryMarketSeg")],
     label = array(ctDF[,c("OnlineTA", "OfflineTATO", "DirectMarketSeg", "GroupMarketSeg", "CorporateMarketSeg", "ComplementaryMarketSeg")]),pos = 3,cex = 0.8)

brplt5 <- barplot(ctDF[,c("Bed&Breakfast", "Halfboard", "Fullboard", "UnknownMeal", "NoMeal")]
                  ,beside =TRUE, ylab = "% of total people", ylim = c(0,110.00))
text(brplt5, y = ctDF[,c("Bed&Breakfast", "Halfboard", "Fullboard", "UnknownMeal", "NoMeal")],
     label = array(ctDF[,c("Bed&Breakfast", "Halfboard", "Fullboard", "UnknownMeal", "NoMeal")]),pos = 3,cex = 0.8)

```

Checking if the reserved and assigned rooms make any difference to the cancellation.
```{r}
# Most cancelled type of assigned room
tbl1 <- table(db_c[,c("AssignedRoomType", "IsCanceled")])
tbl1
# Most cancelled type of room reserved by the customers
table(db_c[,c("ReservedRoomType", "IsCanceled")])

# Making boolean column wherein reserved rooms and assigned rooms are compared.
db_c$CompareReserveAssign <- db$ReservedRoomType==db$AssignedRoomType

# Checking if the reserved room and assigned room make any difference on cancellation behavior
table(db_c[,c("CompareReserveAssign", "IsCanceled")])
```

```{r}
arm_catDB <- db_c[,c("IsCanceled", "Meal", "MarketSegment", "IsRepeatedGuest", "DepositType", "CustomerType", "AssignedRoomType", "ReservedRoomType")]
rules <- apriori(arm_catDB,
                  parameter = list(supp=0.005, conf=0.98, minlen=6),
                  appearance = list(default="lhs", rhs=("IsCanceled=1")),
                  control = list(verbose=F))
inspectDT(rules)
```


check if one assigned room changes the outcome when it is different than the reserved one
```{r}
inspectDT(apriori(db_c, 
                parameter = list(conf=0.000025, minlen=2, supp=0.00005),
                  appearance = list(default="lhs", rhs=("IsCanceled=1")),
                  control = list(verbose=F)))
```

```{r}
scplt <- ggplot(db)
scplt1 <- scplt+ aes(x = Adults, y = RequiredCarParkingSpaces) + geom_point()
scplt1
```

